Transient Corotating Clumps Around Adolescent Low-Mass Stars From Four Years of TESS

### 2023-09-02 paper/ms.tex
update ms

% 250 word max!
\begin{abstract}
  We study a set of pre-main-sequence stars
  with sub-solar masses, rotation periods of 0.2--2 days, optical variability amplitudes
  of a few percent, and sharp recurring light curve features that last for
  hundreds of cycles.  The sharp features are probably caused by
  eclipsing clumps of dust or gas orbiting at the corotation radius.
  We refer to this class of variable star as ``complex rotators'' (CRs).
  To improve our understanding of these
  enigmatic objects, we conducted a survey for CRs using TESS
  short-cadence data collected between 2018~July and 2022~September.
  Our search of \nstarssearched\ K and M dwarfs with $T$$<$16 and
  $d$$<$150\,pc yielded \ngoods\ high-quality CRs, most of which are
  new discoveries.  Our sample includes the brightest
  ($T$$\approx$9.5), closest ($d$$\approx$20\,pc), and oldest
  ($\approx$200\,Myr) known CRs.  One of the new discoveries, LP
  12-502, stands out for the complexity of its light curve --- with as
  many as eight flux dips per cycle --- and the detail with which the
  evolution in each dip's amplitude and phase can be tracked over
  1{,}500 cycles.  We argue that corotating gas or dust remains the
  most viable explanation for CRs. The gas or dust is probably
  entrained by the star's magnetic field, and the sharp features may
  result from a multipolar field topology, a hypothesis supported by
  correspondences between the light curves of CRs and of B stars
  known to have strong multipolar magnetic fields.
\end{abstract}

@@

    \item Surprising analogs to the CRs exist in two magnetic B stars
      with multipolar field topologies.  Since most magnetic B stars
      have dipolar magnetic fields, this suggests that the CR dips and
      warps are similarly being sculpted by the stellar magnetic
      fields, and that the magnetic fields themselves are potentially
      also multipolar.

>>>>

% 250 word max!
\begin{abstract}
  We study a set of pre-main-sequence stars
  with sub-solar masses, rotation periods of 0.2--2 days, optical variability amplitudes
  of a few percent, and sharp recurring light curve features that last for
  hundreds of cycles.  The sharp features are probably caused by
  eclipsing clumps of dust or gas orbiting at the corotation radius.
  We refer to this class of variable star as ``complex rotators'' (CRs).
  To improve our understanding of these
  enigmatic objects, we conducted a survey for CRs using TESS
  short-cadence data collected between 2018~July and 2022~September.
  Our search of \nstarssearched\ K and M dwarfs with $T$$<$16 and
  $d$$<$150\,pc yielded \ngoods\ high-quality CRs, most of which are
  new discoveries.  Our sample includes the brightest
  ($T$$\approx$9.5), closest ($d$$\approx$20\,pc), and oldest
  ($\approx$200\,Myr) known CRs.  One of the new discoveries, LP
  12-502, stands out for the complexity of its light curve --- with as
  many as eight flux dips per cycle --- and the detail with which the
  evolution in each dip's amplitude and phase can be tracked over
  1{,}500 cycles.  We argue that corotating gas or dust remains the
  most viable explanation for CRs. The gas or dust is probably
  entrained by the star's magnetic field, and the sharp features could
  result from a multipolar field topology, a hypothesis supported by
  correspondences between the light curves of CRs and of B stars
  that may have strong multipolar magnetic fields.
\end{abstract}

@@

    \item Surprising analogs to the CRs exist in two magnetic B stars,
      one of which is known to have an extreme multipolar field
      topology.  Since most magnetic B stars have dipolar magnetic
      fields \citep{2009ARA&A..47..333D}, this suggests that the CR
      dips and warps are similarly being sculpted by the stellar
      magnetic fields, and that the magnetic fields themselves are
      potentially also multipolar.
